Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-11-25 main.tex
:dizzy: MAC channel by marginal distributions

			On top of this, the decision region of hypothesis $\mathcal{H}_i$ is

@@

			where $\Gamma(\cdot)$ is the gamma function. As such, the equivalent discrete memoryless channel can be defined by a transition matrix where the probability of observing output $j \in \mathcal{M^K}$ under input $i \in \mathcal{M^K}$ is\footnote{For simplicity, we assume all possible input combinations yield distinct energy levels.}

@@

@@

>>>>

			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is

@@

			where $\Gamma(\cdot)$ is the gamma function. Hence, the equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ can be defined by a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}

@@

				\label{eq:equivalent_channel}

@@

			Based on the equivalent point-to-point channel \eqref{eq:equivalent_channel}, we can compute the marginal on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. [ADD EQUATION HERE]

			Mathematically speaking,
			\begin{equation}
				p(z_j \mid c_{m_k}) = \sum_{i_1,\ldots,i_{k-1},i_{k+1},\ldots,i_K} p(z_j \mid \boldsymbol{c}_{i \setminus k}, c_{m_k}) / \sum_{i_1,\ldots,i_K} p(z_j \mid \boldsymbol{c}_i)
			\end{equation}
